Carbonate chemistry at Ny-Ålesund

### 2021-03-24 awipev-CO2.Rmd
Bugs corrected in calculations involving the various formulations of K1K2

  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)

@@

carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 

@@

carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 

@@

carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 

@@

                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 

@@

carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 

@@

                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 

>>>>

  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at, sal_fb, temp_fb)

@@

carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 

@@

carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
